Exploring Uncharted Territories - Predicting Activty Cliffs in Structure-Activity Landscapes

### 2012-07-26 paper.tex
updated some more figs

\ctable[cap={}, caption={Datasets considered in this study. $N_{desc}$ is the number of descriptors
  for the dataset after removal of correlated and low-variance descriptors from the original pool of
109 descriptors.},
label={tab:data}]
{lp{0.3\textwidth}rrrrr}
{}
{\FL
Name & Description & Endpoint & ChEMBL AID & Size & $N_{desc}$ & Reference
\ML
Cavalli & \raggedright{Putative hERG inhibitors (via pharmacophore modeling)} & pIC$_{50}$ &  & 30 & 40 &  Ref.~\citen{Cavalli:2002aa} \NN
Costanzo & \raggedright{Thrombin inhibitors} & $\mathrm{IC_{50}}$ & 305283 & 60 & 21 & 
Ref.~\citen{Costanzo:2005uq} \NN
Kalla & \raggedright{A2B adenosine receptor antagonists} & $429056K_i$ &
364155 & 38 & 10 & Ref.~\citen{Kalla:2006kx} \NN
Dai & \raggedright{RTK inhibitors} & $K_i$ & 429056 & 44 & 12 & Ref.~\citen{Dai:2007kl}
% Mewshaw & \raggedright{ER$\beta$ inhibitors} & $\mathrm{IC_{50}}$ &
% 306229 & 70 & \cite{Mewshaw:2005vf} \NN
\LL}

@@

\ctable[cap={}, caption={The hold out molecules for the Dai dataset
  and training set members with which the hold outs exhibit predicted
  activity cliffs. Bold numbers are ChEMBL MOLREGNO values and numbers
  in parentheses are the absolute prediction
  residual in log(SALI) units.}, figure, botcap,
label={fig:dai-comparison}]    
{c}
{}  
{\includegraphics[width=\linewidth]{dai-comparison}}

>>>>

\ctable[cap={}, caption={Datasets considered in this study. $N_{desc}$ is the number of descriptors
  for the dataset after removal of correlated and low-variance descriptors from the original pool of
109 descriptors.},
label={tab:data}]
{lp{0.3\textwidth}rrrrr}
{}
{\FL
Name & Description & Endpoint & ChEMBL AID & Size & $N_{desc}$ & Reference
\ML
Cavalli & \raggedright{Putative hERG inhibitors (via pharmacophore modeling)} & pIC$_{50}$ &  & 30 & 40 &  Ref.~\citen{Cavalli:2002aa} \NN
Costanzo & \raggedright{Thrombin inhibitors} & $\mathrm{IC_{50}}$ & 305283 & 60 & 21 & 
Ref.~\citen{Costanzo:2005uq} \NN
Kalla & \raggedright{A2B adenosine receptor antagonists} & $K_i$ &
364155 & 38 & 10 & Ref.~\citen{Kalla:2006kx} \NN
Dai & \raggedright{RTK inhibitors} & $K_i$ & 429056 & 44 & 12 & Ref.~\citen{Dai:2007kl}
% Mewshaw & \raggedright{ER$\beta$ inhibitors} & $\mathrm{IC_{50}}$ &
% 306229 & 70 & \cite{Mewshaw:2005vf} \NN
\LL}

@@

\ctable[cap={}, caption={Three of the  hold out molecules for the Dai dataset
  and training set members with which the hold outs exhibit predicted
  activity cliffs. Bold numbers are ChEMBL MOLREGNO values and numbers
  in parentheses are the absolute prediction
  residual in log(SALI) units.}, figure, botcap,
label={fig:dai-comparison}]    
{c}
{}  
{\includegraphics[width=\linewidth]{dai-comparison}}
